Timely Object Recognition

### 2012-05-30 writeups/nips12/nips2012.tex
mean det ap now in final vs. t evaluation, and some minor changes
working on writeup

\begin{abstract}
In a large visual multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy, guided by inference of the contents of the image, to decide which detector to deploy next.
We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
\end{abstract}

\input{../eccv12/introduction.tex} % includes Evaluation section
\input{../eccv12/technical.tex}
\input{../eccv12/evaluation.tex}
\input{../eccv12/related.tex}

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include 
acknowledgments in the anonymized submission, only in the 
final paper.

>>>>

\begin{abstract}
In a large visual multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy guided by inference of the contents of the image to decide which detector to deploy next.
We evaluate with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC object detection dataset.
\end{abstract}

\input{introduction.tex} % includes Evaluation section
\input{related.tex}
\input{technical.tex}
\input{evaluation.tex}

% \subsubsection*{Acknowledgments}
% Use unnumbered third level headings for the acknowledgments. All
% acknowledgments go at the end of the paper. Do not include 
% acknowledgments in the anonymized submission, only in the 
% final paper.

### 2012-05-30 writeups/nips12/related.tex
started working on related work
working on writeup

\section{Related Work}

under construction

The literature on object detection is vast.
Here we briefly summarize detection work that sufficiently contextualizes our contribution in the areas of object classification and detection in context, saliency, multi-class prediction, steering of computation (such as in cascades, any time algorithm) and active classification.

>>>>

\section{Recognition Problems and Related Work}

We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.

The multi-class, multi-label \textbf{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $k$.
We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $k$ is present.

The \textbf{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $k$, for each $k$.
The answer for a single class is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.

The answer is evaluated by plotting precision vs. recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive detection).
The area under the curve yields the Average Precision (AP) metric, which has become the standard evaluation for recognition performance on challenging datasets in vision \cite{pascal-voc-2010}.
A common measure of a correct detection is the PASCAL overlap: two bounding boxes are considered to match if they have the same label and the ratio of their intersection to their union is at least $\frac{1}{2}$.

To highlight the hierarchical structure of these problems, we note that (1) the confidences for each sub-image $b \in B$ may be given by $\emph{classify}(b,k)$; (2) correct answer to the detection problem also answers the classification problem.

\subsection{Related Work}
The literature on object detection is vast.
Here we briefly summarize detection work that sufficiently contextualizes our contribution in the areas of object classification and detection in context, saliency, multi-class prediction, steering of computation (such as in cascades, any time algorithm) and active classification.

### 2012-05-30 writeups/nips12/technical.tex
working on writeup

\section{Recognition Problems}

We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.

The multi-class, multi-label \textbf{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $k$.
The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},k)$.
We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $k$ is present.

The answer is evaluated by plotting precision vs. recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive label) and integrating to yield the Average Precision (AP) metric, which has become the standard evaluation for recognition performance on challenging datasets \cite{pascal-voc-2010}.

\comment{
We can make the classification problem more difficult by posing the \emph{counting} problem, which asks how many objects of class $k$ are present in $\mathcal{I}$, for each $k$.
This setting is not commonly evaluated; we mention it for its usefulness in later exposition.
}

The \textbf{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $k$, for each $k$.
The answer for a single class is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.

A common measure of a correct detection is the PASCAL overlap: two bounding boxes are considered to match if they have the same label and the ratio of their intersection to their union is at least $\frac{1}{2}$.
Again, Average Precision is the single-number metric for the performance of a detector.

As our task is fundamentally in \emph{multi-class} object detection, we rely on a slightly different evaluation than is commonly used (although it has precedent in \cite{Desai2009}).
Instead of pooling detections across images in the dataset, and considering classes individually, we pool detections across classes, but consider images individually, reporting results averaged across the dataset.

To highlight the hierarchical structure of these problems, we note that (1) the confidences for each sub-image $b \in B$ may be given by $\emph{classify}(b,k)$; (2) the correct answer to the detection problem also answers the classification problem. \comment{the counting and classification problems}

Our goal is a general recognition policy that outputs both classification and detection results; we evaluate on both tasks.

@@

As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and then outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.

The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, potentially receives an observation $o_i$, and selects the next action.
The set of actions can include classifiers, detectors, or hybrid actions (detector followed by classification of its output).

A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the actions.
This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or decision trees.

Let $\mathcal{A}$ consist of $K$ detectors $L^\text{det}_i$.
We use one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.

\comment{Let $\mathcal{A}$ consist of $K$ actions:
\begin{itemize}
  \item $K$ detectors $L^\text{det}_i$: one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.
  \item $K$ classifiers $L^\text{gist}_i$: one-vs-all SVMs on the GIST feature \cite{Torralba2004}.
\end{itemize}}

\subsubsection{Time and Evaluation}
Each action $L$ has an expected cost $c(\cdot)$ of execution.
Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.

@@

A single-number metric that corresponds to this objective is simply the ratio of the area captured under the curve to the total area between the start and deadline bounds.
\comment{Just like the metric of Average Precision itself was motivated by the inadequacy of any single Precision-Recall operating point to describe the performance of a robust system, our proposed metric is motivated by the inadequacy of any single Performance vs. Time operating point.}
We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason that Average Precision is used instead of a fixed Precision vs. Recall point.

\subsubsection{Sequential Execution}
An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.
The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
We refer to the current set of observations as $\mathbf{o} = \{o_i | L_i \in \mathcal{O}\}$.

>>>>

@@

Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results $\emph{detect}(I)$ by running detector and other \emph{actions} sequentially.

The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, receiving observations $o_i$, and then selects the next action.
The set of actions can include both classifiers and detectors: anything that would be useful for inferring the contents of the image.

Each action $a_i$ has an expected cost $c(a_i)$ of execution.
Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.

@@

A single-number metric that corresponds to this objective is simply the ratio of the area captured under the curve to the total area between the start and deadline bounds.
We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason that Average Precision is used instead of a fixed Precision vs. Recall point.

\subsubsection{Sequential Execution}
An ``open-loop'' policy takes actions in a sequence that does not depend on observations received from previous actions.
The common classifier cascade \cite{Viola2001} is an example.
In contrast, our goal is to learn a dynamic, or ``closed-loop,'' policy, which would exploit the signal in inter-object and scene context for a maximally efficient path through the actions.

An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.
The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
We refer to the current set of observations as $\mathbf{o} = \{o_i | L_i \in \mathcal{O}\}$.
